Manuscript Draft

### 2019-01-10 manuscript.tex
update manuscript, fix table, venndiagrams

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Manuscript Draft},
            pdfauthor={Sally E. Claridge, Daniel M. Charytonowicz, \& Adam A. Margolin},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\subsection{Comparison of G2P drug-gene associations and CCLE, CTRP, and
GDSC}\label{comparison-of-g2p-drug-gene-associations-and-ccle-ctrp-and-gdsc}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table-g2p-nonCID}Distribution of level-A G2P drugs excluded from analyses}
\begin{tabular}{llll}
\toprule
Compound & \multicolumn{1}{c}{Compound identifier} & \multicolumn{1}{c}{Number of G2P interpretations} & \multicolumn{1}{c}{Proportion of excluded interpretations (\%)}\\
\midrule
cetuximab & CHEMBL1201577 & 74 & 18.41\\
cisplatin & CHEMBL2068237 & 3 & 0.75\\
EGFR & SID160769799 & 1 & 0.25\\
ipilimumab & CHEMBL1789844 & 2 & 0.50\\
mAb & CHEMBL2109423 & 16 & 3.98\\
nivolumab & CHEMBL2108738 & 4 & 1.00\\
panitumumab & CHEMBL1201827 & 75 & 18.66\\
pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
pertuzumab & CHEMBL2007641 & 1 & 0.25\\
trastuzumab & CHEMBL1201585 & 9 & 2.24\\
NA & NA & 214 & 53.23\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

Using cell-line-specific point mutation annotations from the CCLE, we
compared z-score-transformed area under the dose-response curve (AUC)
distributions between mutant and wildtype cell lines for all G2P genes
for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
(\emph{Figures 1B and 2A}). At an unadjusted \(\alpha = 0.05\), Wilcoxon
rank-sum tests revealed that in CCLE, the AUC distributions of mutant
and wildtype groups for 18 out of 170 (10.59\%) tested drug-gene
combinations were significantly different, 135 out of 918 (14.71\%) were
significantly different for CTRP, and 89 out of 850 (10.47\%) for GDSC.

Controlling for a false discovery rate (FDR) \textless{} 5\%,
selumetinib-\emph{BRAF} (\(p\) \textless{} .001) was the only
significant drug-gene combination tested in CCLE (\(p_k < 8^{-4}\)).
CTRP (\(p_k < 7^{-4}\)) yielded 918 significant combinations, one of
which was selumetinib-\emph{BRAF}.

@@

We computed Spearman correlation coefficients (\(r_s\)) between AUC of
each drug-gene association and gene expression (RPKM) and copy number
(log\(_2\) ratio) of the gene in the association

@@

\begin{itemize}
\tightlist
\item
  What do these correlations with mutation status, gene expression, and
  copy number look like when you constrict to a specific lineage?
\item
  When you restrict, do the correlations become more distinct?
\item
  Are the lineage-specific results approximately the same as the
  pancancer results?
\item
  Looking at a histogram of p-values, if the histogram is flat, then
  nothing is significant (note from meeting on 11/16)
\end{itemize}

@@

@@

When we don't account for lineage, Wilcoxon rank-sum tests
(\(p_k < 5^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
genes significantly correlated with CERES score: \emph{KRAS} (\(p\)
\textless{} .001) and \emph{BRAF} (\(p\) \textless{} .001).

Gene expression (RPKM) of 12 out of 33 (36.36\%) G2P genes significantly
correlated with CERES score, as did copy number (log2-ratio) for 12 out
of 33 (36.36\%) G2P genes.

>>>>

\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Manuscript Draft},
            pdfauthor={Sally E. Claridge, Daniel M. Charytonowicz, \& Adam A. Margolin},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{lineno}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:table-g2p-nonCID}Level-A G2P interpretations excluded from analyses}
\small{
\begin{tabular}{cccc}
\toprule
Compound & \multicolumn{1}{c}{CID} & \multicolumn{1}{c}{N\_G2P} & \multicolumn{1}{c}{\%}\\
\midrule
EGFR & SID160769799 & 1 & 0.25\\
pertuzumab & CHEMBL2007641 & 1 & 0.25\\
ipilimumab & CHEMBL1789844 & 2 & 0.50\\
cisplatin & CHEMBL2068237 & 3 & 0.75\\
pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
nivolumab & CHEMBL2108738 & 4 & 1.00\\
trastuzumab & CHEMBL1201585 & 9 & 2.24\\
mAb & CHEMBL2109423 & 16 & 3.98\\
cetuximab & CHEMBL1201577 & 74 & 18.41\\
panitumumab & CHEMBL1201827 & 75 & 18.66\\
NA & NA & 214 & 53.23\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} N\_G2P (\%) = number of associated G2P interpretations, \% is out of column total; mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\textbf{Describe why we compare all pairwise combos rather than
filtering for just the drug-gene combos in G2P}

Using cell-line-specific point mutation annotations from the CCLE, we
compared z-score-transformed area under the dose-response curve (AUC)
distributions between mutant and wildtype cell lines for all pairwise
combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC
drug screens (\emph{Figures 1B and 2A}). At an unadjusted
\(\alpha = 0.05\), Wilcoxon rank-sum tests revealed that in CCLE, AUC
significantly correlated with mutation status for 18 out of 170
(10.59\%) tested drug-gene combinations were significantly different,
135 out of 918 (14.71\%) were significantly different for CTRP, and 89
out of 850 (10.47\%) for GDSC.

Controlling for a false discovery rate (FDR) \textless{} 5\%,
selumetinib-\emph{BRAF} (\(p_{adj} = 1.4^{-10}\)) was the only
significant drug-gene combination tested in CCLE (\(p_k = 7.9^{-4}\)).
CTRP (\(p_k = 6.5^{-4}\)) yielded 5 significant combinations, one of
which was selumetinib-\emph{BRAF}. There were 3 significant G2P
associations in the GDSC dataset (\(p_k = 9.5^{-5}\)), Of all the
significant correlations between mutation status and AUC across
datasets, the only genes represented were \emph{KRAS} and \emph{BRAF}
(Figure~\ref{fig:drug-venn}).

\begin{verbatim}
## NULL
\end{verbatim}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/drug-venn-1.pdf}
\caption{}
\end{figure}

@@

We computed Spearman correlation coefficients (\(r_s\)) between AUC of
each drug-gene association and gene expression (RPKM) and copy number
(log\(_2\) ratio) of the gene in the association\ldots{}

@@

\begin{itemize}
\tightlist
\item
  What do these correlations with mutation status, gene expression, and
  copy number look like when you constrict to a specific lineage?
\item
  When you restrict, do the correlations become more distinct?
\item
  Are the lineage-specific results approximately the same as the
  pancancer results?
\item
  Looking at a histogram of p-values, if the histogram is flat, then
  nothing is significant (note from meeting on 11/16)
\item
  KS test results
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/crispr-venn-1.pdf}
\caption{}
\end{figure}

@@

When we don't account for lineage, Wilcoxon rank-sum tests
(\(p_k = 5.1^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
genes significantly correlated with CERES score: \emph{KRAS}
(\(p_{adj} = 2.6^{-37}\)) and \emph{BRAF} (\(p_{adj} = 8.2^{-18}\)).
Gene expression (RPKM) of 12 out of 33 (36.36\%) G2P genes significantly
correlated with CERES score, as did copy number (log2-ratio) for 12 out
of 33 (36.36\%) G2P genes (Figure~\ref{fig:crispr-venn}).
